---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rsm.panel

<!-- badges: start -->

<!-- badges: end -->

The objective of Rsm.panel is to offer a Shiny panel featuring response surface methods. This is achieved by allowing users to specify the dependent and independent variables of the uploaded dataset. The function further provides various first- and second-order models, both with and without interaction terms. Additionally, Rsm.panel furnishes insights into the optimal region of the surface and its corresponding location.

## Installation

You can install the development version of Rsm.panel like so:

``` r
# install.packages("devtools")
devtools::install_github("nelsonabadz/Rsm.panel")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Rsm.panel)
# Execute the function and provide the dataset. That's all!
# Function: Rsm.panel()
```
